---
title: "Extracting Data from Human Activity Recognition Using Smartphones Dataset"
output: md_document
---

The code in this repository operates on the Human Activity Recognition Using Smartphones Dataset Version 1.0 from Davide Anguita, Alessandro Ghio, Luca Oneto, Xavier Parra and Jorge L. Reyes-Ortiz. Human Activity Recognition on Smartphones using a Multiclass Hardware-Friendly Support Vector Machine. International Workshop of Ambient Assisted Living (IWAAL 2012). Vitoria-Gasteiz, Spain. Dec 2012

The run_analysis.R script contains commands to perorm the following transformations.

Read in sensor data, merging train and test content
```{r}
dataX <- rbind(read.table("UCI HAR Dataset/train/X_train.txt"), read.table("UCI HAR Dataset/test/X_test.txt"));
```

Read in activity label data, merging train and test content
```{r}
dataY <- rbind(read.table("UCI HAR Dataset/train/y_train.txt"), read.table("UCI HAR Dataset/test/y_test.txt"));
```

Read in subject data, merging train and test content
```{r}
subjects <- rbind(read.table("UCI HAR Dataset/train/subject_train.txt"), read.table("UCI HAR Dataset/test/subject_test.txt"));
```

Read in the descriptive names of the activities
```{r}
activityLabels <- read.table("UCI HAR Dataset/activity_labels.txt");
```

Create a factor with descriptive activity names out of the activity label data
```{r}
dataYLabels <- NULL;
dataYLabels$Activity <- factor(dataY$V1, labels = activityLabels[, 2], ordered = F);
```

Read in the descriptive names of the features
```{r}
featureNames <- read.table("UCI HAR Dataset/features.txt");
```

Create a unified data set starting with the activity lable data
```{r}
data <- as.data.frame(dataYLabels);
```

…continuing with the subjects
```{r}
data$Subject <- subjects$V1;
```

…and adding the mean and standard deviation variable observations, using descriptive variable names
```{r}
data[make.names(featureNames$V2[grep("mean\\(|std", featureNames$V2)])] <- dataX[grep("mean\\(|std", featureNames$V2)]
```


Detailed information on the included variables is avialable in CodeBook.md
